NLTK: The Natural Language Toolkit

### 2002-05-15 technical/acl2002/acl02.tex
ran ispell, added my hyphenation rules, enlarged cascade displays, other minor editorial corrections, acknowledgements
svn/trunk@620

%
% Submission for ``Effective Tools And Methodologies For Teaching
% Natural Language Processing And Computational Linguistics'' workshop
% at ACL 2002
%
% Authors: Edward Loper and Steven Bird
% 
% $Id$
%
\documentclass[11pt]{article}
\usepackage{acl2002,url,alltt,epsfig}
\title{NLTK: The Natural Language Toolkit}
\author{
Edward Loper and Steven Bird\\
Department of Computer and Information Science \\
University of Pennsylvania, Philadelphia, PA 19104-6389, USA
}
\date{}

% To do:
%   - Add acknowledgements

@@

\newenvironment{sv}{\scriptsize\begin{alltt}}{\end{alltt}\normalsize}

@@

The Natural Language Toolkit is available under an open source license
from \mbox{\url{http://nltk.sf.net/}}.  NLTK runs on most platforms, including
Windows, OS X, Linux, and Unix.

@@

% Less grunt-work
NLTK eliminates the tedious infrastructure-building that is typically
associated with advanced student projects, by providing students with
the basic data structures, tools, and interfaces that they need.  This
allows the students to concentrate on the problems that interest them.

@@

% Good examples
Finally, many of the modules included in the toolkit provide students
with good examples of what projects should look like, with well
thought out interfaces, clean code structure, and thorough
documentation.

@@

Finding suitable corpora is a prerequisite for many student
assignments and projects.  We are therefore putting together a
standard collection of large, clean, open-source corpora, containing
data appropriate for every module defined by the toolkit.

@@

\emph{Add acknowledgements: reviewers; funders; students of 530;
others?}

>>>>

%
% Submission for ``Effective Tools And Methodologies For Teaching
% Natural Language Processing And Computational Linguistics'' workshop
% at ACL 2002
%
% Authors: Edward Loper and Steven Bird
% 
% $Id$
%
\documentclass[11pt]{article}
\usepackage{acl2002,url,alltt,epsfig}

% hyphenation control
\pretolerance 250
\tolerance 500
\hyphenpenalty 200
\exhyphenpenalty 100
\doublehyphendemerits 7500
\finalhyphendemerits 7500
\brokenpenalty 10000
\lefthyphenmin 3
\righthyphenmin 3
\widowpenalty 10000
\clubpenalty 10000
\displaywidowpenalty 10000
\looseness 1

\title{NLTK: The Natural Language Toolkit}
\author{
Edward Loper and Steven Bird\\
Department of Computer and Information Science \\
University of Pennsylvania, Philadelphia, PA 19104-6389, USA
}
\date{}

@@

\newenvironment{sv}{\small\begin{alltt}}{\end{alltt}\normalsize}

@@

The Natural Language Toolkit is available under an open source license
from \mbox{\url{http://nltk.sf.net/}}.  NLTK runs on all platforms
supported by Python, including Windows, OS X, Linux, and Unix.

@@

% Less grunt-work
NLTK eliminates the tedious infrastructure-building that is typically
associated with advanced student projects by providing students with
the basic data structures, tools, and interfaces that they need.  This
allows the students to concentrate on the problems that interest them.

@@

% Good examples
Finally, many of the modules included in the toolkit provide students
with good examples of what projects should look like, with well
thought-out interfaces, clean code structure, and thorough
documentation.

@@

Finding suitable corpora is a prerequisite for many student assignments and
projects.  We are therefore putting together a collection of corpora
containing data appropriate for every module defined by the toolkit.

@@

We are indebted to our students for feedback on the toolkit,
and to anonymous reviewers and the workshop organizers for comments
on an earlier version of this paper.  We are grateful to Mitch
Marcus and the Department of Computer and Information Science
at the University of Pennsylvania for sponsoring the work
reported here.
